---
title: "BebxVLxSimulateDrugExposureAttempt"
author: "ehe"
date: "2023-09-22"
output: html_document
---
#Load in necesary packages, notable rxode2, tidyverse. 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(pkgbuild) #checks if compiler is present. Compiler is mandatory for RxODE
library(devtools)
pkgbuild::has_build_tools(debug = TRUE) #checks if you have a working C compiler
library(rxode2)
```

#Set up Simple Exp/decay ODE model with 1-cmpt first and assess ratio of n_mAb:#n_virions
#TCLE model adopted from Goncalves  
```{r exponential growth/decay model with BEB}
# Add the Effect term into your viral dynamics equation 
ode_beb_dcdt <- "
        a = log(Smax / S0) / tp;
B = log(Smax / S0) / (tf - tp);
        Effect = ((C_ss) / (IC50 + C_ss));
        d/dt(C_ss) = -k*C_ss;
        if (0 <= t && t < tp) {
  d/dt(S) = a * S * (1 - Effect);
} else {
  d/dt(S) = -B * S;
}
"
```


#Provide theta for the parameters outlined in ODE 
```{r theta for Bebtelovimab}
theta.simplebebv1 =c(
        Smax = (10^10)*30,
        S0 = 10^3,
        tf = 14,
        tp = 3,
        IC50 = 0.39, #nM
        C_ss = 3.7361, #538 mg/L converted to 3.7361 nM
        k = 0.06, #.693/11.5 days
        Vt = 4.55 #Liters 
)
```


#Create and solve the model 
```{r model,message=FALSE}
model.bebv1 <- RxODE(model = ode_beb_dcdt, modName = "BEBdcdt")
time_bebv1 <- seq(0, theta.simplebebv1["tf"], by = 1)
vlbebdfv1 <- rxSolve(model.bebv1, 
                     params = theta.simplebebv1,
                     events = data.frame(time = time_bebv1),
                     inits = c(S=1e3*30,C_ss=3.7461))

```


#Overview of dataset constructed; this is the same as VLxTime
```{r dataset}
vlbebdf_tibblev1 <- as_tibble(vlbebdfv1)
head(vlbebdf_tibblev1)
str(vlbebdf_tibblev1)

```

#Convert concentration-time values to number of molecules in new df. Observe contents of df. 
```{r}
avogadro_number <- 6.02*10^23
Vt <- 4.55
vlbebdf_tibblev1.1 <- vlbebdf_tibblev1 %>% 
        mutate(nmol = C_ss*Vt*avogadro_number)
head(vlbebdf_tibblev1.1)
```


#[Beb] x time
```{r graph}
bebconc<-ggplot(data=vlbebdf_tibblev1,
       aes(x=time, y=C_ss))+
        geom_line(linewidth=0.75)+
        xlab("Time (days)")+
        ylab("Log [Bebtelovimab]")+
        ggtitle("Concentration-time profile of BEB in 1-cmpt model")+
         scale_x_continuous(breaks=seq(0,14,by=1),limits=c(0,14))+
        scale_y_log10()+
        theme_bw()
bebconc
```

#nBeb x time
```{r graph}
bebnmol<-ggplot(data=vlbebdf_tibblev1.1,
       aes(x=time, y=nmol))+
        geom_line(linewidth=0.75)+
        xlab("Time (days)")+
        ylab("Number of BEB molecules")+
        ggtitle("1-cmpt BEB exposure in patients")+
         scale_x_continuous(breaks=seq(0,14,by=1),limits=c(0,14))+
        scale_y_log10()+
        theme_bw()
bebnmol
```

#Plot both Spike Protein (affected by drug) and number of molecules for drug w 2 y-axes 
```{r}
#Implement scale factor b/c the values between both DV are vastly different 
beb_sf<- max(vlbebdf_tibblev1.1$S)/max(vlbebdf_tibblev1.1$nmol)

p_bebnmol_vl <- ggplot(data = vlbebdf_tibblev1.1,
                       aes(x=time))+
        geom_line(aes(y=S),color="black")+
        geom_line(aes(y=nmol*beb_sf),color="skyblue",linewidth=1)+
        scale_y_log10(sec.axis = sec_axis(~./beb_sf, name = "Number of BEB Molecules"))+
        scale_x_continuous(breaks=c(0:14))+
        ylab("Number of Spike Protein")+
        xlab("Time (days)")+
        ggtitle("nBEB molecules and COVID-19 Spike Protein over Time")+
        theme_bw()
p_bebnmol_vl
        
#suggests that BEB isn't removed after 14 days; PK study identified notable amounts after 270 days
```

#Save the plot into its respective directory 
```{r}

```

