---
title: "SPxTime"
author: "ehe"
date: "2023-09-20"
output: html_document
---
#Load in necesary packages, notable rxode2, tidyverse. 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(pkgbuild) #checks if compiler is present. Compiler is mandatory for RxODE
library(devtools)
pkgbuild::has_build_tools(debug = TRUE) #checks if you have a working C compiler
library(rxode2)
```

#Set up Simple Exp/decay ODE model with 1-cmpt first and assess how well it fits our data from PNAS 
#TCLE model adopted from Goncalves  
```{r exponential growth/decay model}
#Try solving for change of V over time 
ode_dSPdt <- "
 a = log(Smax / S0) / tp;
B = log(Smax / S0) / (tf - tp);
        if (0 <= t && t <= tp) {
            d/dt(S) = a * S;
        } else {
            d/dt(S) = -B * S;
        }
"
```

#Set Initial Estimates 
```{r IE}
theta.SPexpdecay = c(
        Smax = (10^10)*30, # maximal number of virions * conversion factor to obtain maximum spike proteins availaible 
        S0 = (10^3)*30,   # number of virions at time of infection
        tf = 14,     # average duration of infection, range 10 - 15 days
        tp = 3       # peak load seen 2 - 4 days post-inoculation
)
```

#Set Initial Conditions: start from time = 0 to 14 
```{r IC}
initial_SP <- c(V = theta.SPexpdecay["S0"])
```


#Create and solve the model 
```{r model}
model.spikeprotein <- RxODE(model = ode_dSPdt, modName = "basicSPmodel")
time_sp <- seq(0, theta.SPexpdecay["tf"], by = 0.001)
SP_df <- rxSolve(model.spikeprotein, 
                     params = theta.SPexpdecay,
                     events = data.frame(time = time_sp),
                     inits = c(S=(10^3)*30))
```

#Overview of dataset created, SP_df
```{r header SP_df}
SP_tibble<-as_tibble(SP_df)
head(SP_tibble)
str(SP_tibble)
```

#Plot Log[Spike Protein] over Time; should observe identical curvature with earlier models 
```{r ggplot}
sp_control<- ggplot(data=SP_tibble,
                    aes(x=time,y=S))+
        geom_line(linewidth=0.5)+
        geom_point(size=0.5)+
        scale_y_log10(breaks=c(30000, (10^10)*30))+
        scale_x_continuous(breaks=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14),limits=c(0,14))+
        ggtitle("Change in Log[Spike Protein] over Time ")+
        xlab("Time (days)")+
        ylab("Log [Spike Protein]")+
        theme_bw()
sp_control
```


#Save the plot
```{r save the plot with custom dimensions}
ggsave("SPxTime.png",plot=sp_control,width=5,height=3,dpi=600)
```


